Non-word repetition in Yélî Dnye

### 2022-02-21 manuscript.Rmd
minor, addressing Rs
for ldr stylesheet

lang              : "en-US"
class             : "man"
output            :
  papaja::apa6_pdf:
    latex_engine: xelatex
    includes:
      in_header: header.tex
---

@@

kable(stims.wide,
  "latex", booktabs = T,
  caption="NWR stimuli in orthographic (Orth.) and phonological (Phon.) representations.",
  row.names =F) %>%
  kable_styling(latex_options = "HOLD_position") %>%
  add_header_above(c("Practice" = 2, "Monosyll" = 2,
    "Bisyll" = 2, "Trisyll" = 2, "Tetrasyll" = 2))

@@

kable(mytab,
  "latex", booktabs = T,
  caption="Number (and percent) of vowel targets that were correctly repeated (Corr.), deleted (Del.), or substituted, as a function of vowel type, and whether the error resulted in a nasality change (Nasal Err.) or only a quality change (Qual. Err.)")

@@

kable(mytab,
  "latex", booktabs = T,
  caption="Number (and percent) of consonant targets that were correctly repeated (Corr.), deleted (Del.), or substituted, as a function of the complexity of the consonant, and whether the error resulted in a change of complexity (Cmpl Err.) or not (Othr Err.)")

>>>>

lang              : "en-US"
class             : "man"
output            :
  papaja::apa6_word:
    latex_engine: xelatex
    includes:
      in_header: header.tex
---

@@

kable(stims.wide,
  "latex", booktabs = T,
  caption="NWR stimuli in orthographic (Orth.) and phonological (Phon.) representations.",
  row.names =F) %>%
  kable_styling(latex_options = "HOLD_position") %>%
  add_header_above(c("Practice" = 2, "Monosyll" = 2,
    "Bisyll" = 2, "Trisyll" = 2, "Tetrasyll" = 2))
write.csv(stims.wide,"tab1.csv")
```

@@

kable(mytab,
  "latex", booktabs = T,
  caption="Number (and percent) of vowel targets that were correctly repeated (Corr.), deleted (Del.), or substituted, as a function of vowel type, and whether the error resulted in a nasality change (Nasal Err.) or only a quality change (Qual. Err.)")
write.csv(mytab,"tab2.csv")
```

@@

kable(mytab,
  "latex", booktabs = T,
  caption="Number (and percent) of consonant targets that were correctly repeated (Corr.), deleted (Del.), or substituted, as a function of the complexity of the consonant, and whether the error resulted in a change of complexity (Cmpl Err.) or not (Othr Err.)")
write.csv(mytab,"tab3.csv")
```
